\section{Introduction}
\label{sec::intro}

Many instances of constraint optimization problems
remain challenging to current technology.
In such problems, the task is to find a solution
(e.g., assignment to variables that define a state) 
that satisfies a number of constraints specified in the definition
of the problem, while optimizing an objective function
(e.g., maximizing a score or minimizing a cost).

We focus on the Romanian Crosswords Competition Problem ({\sc Roco} for short),
introduced in the search literature by
\citeauthor{DBLP:conf/socs/BoteaB21}~\shortcite{DBLP:conf/socs/BoteaB21}.
The application has a decades-long history of annual national-level competitions among humans.
The problem is challenging to Artificial Intelligence (AI) which has been lagging significantly
behind the performance of top human contestants,
despite recent progress~\cite{DBLP:conf/socs/BoteaB21,DBLP:conf/cig/BulitkoB21,Botea_Bulitko_2022}.

In {\sc Roco} the input includes two lists of words (the thematic list and the regular list)
and a $13 \times 13$ grid with white cells.
The task is to fill the grid with criss-crossing words and no more than 26 black cells.
Each thematic word gives a number of points equal to its length. The objective
is to obtain as many points as possible.

We present an approach that first builds a \emph{core},
a part of the problem that will have a strong contribution
to the score (objective function) of the solution.
A core is utilized to build a partial solution called a {\em seed}.
%A seed has part of the state variables specified and instantiated.
A seed is further evolved into a {\em full solution}, in a way that aims
at maximizing the overall score.

{\sc Roco} generalizes a well-known problem that we
call the {standard crosswords grid generation}.
The latter is a textbook example of a constraint satisfaction problem.
The input is a list of words, and a grid with black cells and white cells.
The task is to fill the white-cell area with criss-crossing words.

{\sc Roco} generalizes the standard crosswords grid generation in two ways
and the resulting differences amplify the computational difficulty of {\sc Roco} in practice.
Firstly, in {\sc Roco}, solutions are ranked by their score,
whereas in the standard problem any correct solution will do.
Often finding a high-quality solution is much more challenging than finding any solution.
Secondly, the task in {\sc Roco} includes finding a configuration of black cells
(that will allow achieving a high score) whereas in standard grid
generation the configuration of black cells is given as input.
The absence of a pre-existing black cell configuration
combinatorially increases the search space and good configurations
(i.e., that allow achieving a high score) are difficult to find.

%Recent work in {\sc Roco} showed that state-of-the-art AI significantly lags behind
%top human performance, despite a significant recent progress.

Our approach takes as input the size of a rectangular core
and the locations of zero or more black cells inside the core.
We report a substantial improvement of the scores achieved compared
to previous work.
Our system is capable of generating scores in the vicinity of human champion scores.
We feel that the approach presented in this paper may be a breakthrough towards achieving the long-standing goal of outperforming human champions in this challenging domain.